2-rules

### 2017-11-20 analysis/analyses/3-score_rules/2-rules.Rmd

@@

# summarize the scores
scores2_summary <- scores2 %>% gather(score_id, score, -toy_id, -comparison) %>%
  spread(comparison, score) %>% mutate(
    score=`gs-toy`,
    diff= `gs-toy`-`gs-gs`,
    frac=`gs-toy`/`gs-gs`
  ) %>% select(-`gs-toy`, -`gs-gs`) %>% left_join(toys, by="toy_id")

@@

## Grouping cells
```{r}
scores_summary %>% ggplot() + geom_point(aes(score, score_grouped, color=generator_id)) + facet_wrap(~score_id)

scores_summary %>% group_by(score_id) %>% summarise(
  cor = cor(score, score_grouped),
  rms = sqrt(sum((score - score_grouped)^2)),
  rms_shifted = sqrt(sum((score - mean(score) - score_grouped + mean(score_grouped))^2))
)
```

>>>>

```{r}
library(tidyverse)
library(dyneval)
```

@@

# summarize the scores
scores2_summary <- scores2 %>% gather(score_id, score, -toy_id, -comparison) %>%
  spread(comparison, score) %>% mutate(
    score=`gs-toy`,
    diff= `gs-toy`-`gs-gs`,
    frac=`gs-toy`/`gs-gs`,
    score_grouped = `gs_groupid-toy`
  ) %>% select(-`gs-toy`, -`gs-gs`) %>% left_join(toys, by="toy_id")

@@

## Grouping cells
```{r}
check_grouping(scores_summary)

plot_grouping(scores_summary)
```
